Effect of Beam Chromaticity on Foregrounds in Wide-Field Measurements of Redshifted 21~cm Power Spectra

### 2016-03-02 ForegroundSimulations/ms.tex
Add two references to bioliography file
From 0e115e5 (restructure):
==========================

In eor.bib,

(*) Add references to Neben et al.(2016) and Ewall-Wice et al.(2016)

In a related series of papers, Neben et~al. (2016; submitted) discuss the agreement of these simulated antenna beam patterns with actual measurements and Ewall-Wice et~al. (2016; submitted) model the reflections and return loss expected in the proposed antenna-receiver assembly. Our focus in this paper is to investigate chromaticity of antenna power patterns from the point of view of their impact on foreground contamination in delay power spectra.

>>>>

In a related series of papers, \citet{neb16} discuss the agreement of these simulated antenna beam patterns with actual measurements and \citet{ewa16} model the reflections and return loss expected in the proposed antenna-receiver assembly. Our focus in this paper is to investigate chromaticity of antenna power patterns from the point of view of their impact on foreground contamination in delay power spectra.
